Appendix of Bauer et al. (2023) Journal of Applied Ecology

### 2023-08-03 manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

---
title: "Appendix of Bauer et al. (2023) bioRxiv"
author: Markus Bauer*, Jakob K. Huber, Johannes Kollmann
output:
  officedown::rdocx_document:
    reference_docx: template_word.docx
csl: template_references_j_appl_ecol.csl
bibliography: bibliography.bib
---

@@

All sown seed mixtures can be found on GitHub in the folder **'outputs/tables/ table_a2_seed_mixtures.csv'**. <!--# Cite Zenodo--> There, we indicate which species were combined and their respective ratio in the specific seed mixture.

@@

All species which occurred 2018--2021 and the amount of plots in which they appeared (maximum 1152 = 4 years times 288 experimental plots). In total, 274 different species were found of which 93 were seeded. The shades of grey indicate the amount of established plots.

>>>>

---
title: "Appendix of Bauer et al. (2023) Journal of Applied Ecology"
author: Markus Bauer*, Jakob K. Huber, Johannes Kollmann
output:
  officedown::rdocx_document:
    reference_docx: template_word.docx
csl: template_references_j_appl_ecol.csl
bibliography: bibliography.bib
---

@@

All sown seed mixtures can be found on GitHub in the folder **'outputs/tables/ table_a2_seed_mixtures.csv'** [@bauer2023experiment]. There, we indicate which species were combined and their respective ratio in the specific seed mixture.

@@

All species which occurred 2018--2021 and the amount of plots in which they appeared (maximum 1152 plots = 4 years times 288 experimental plots). In total, 274 different species were found of which 93 were seeded. The shades of grey indicate the amount of established plots.
